Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-09 sas2015/content/appendix.tex
add section numbers to appendix

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{sec:occur}, and the code discussed in Section~\ref{sec:collex}.

\subsection*{Correlated Calls Occurrences}
Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.
\input{tables/stats}

\subsection*{\code{TraversableOnce} Trait from Scala Standard Library}
Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.

@@

\subsection*{Proofs}

\subsubsection*{Representation of Micro Functions}
We start by presenting the proofs to the lemmas about the representation of micro functions.

@@

\subsubsection*{Efficiency}
We will next introduce the complexity proof for the correlated-calls algorithm.
To satisfy the complexity requirements of the IDE algorithm, we need to provide
an implementation of the IDE lattice and micro-functions that satisfy the following
list of criteria~\cite{sagiv1996precise}:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
\efficient*
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice~\cite{nielson1999principles}.

@@

\subsubsection*{Soundness and Precision}

@@

\subsubsection*{Correlated-Call Receivers}
We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.

>>>>

\section{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{sec:occur}, and the code discussed in Section~\ref{sec:collex}.

\subsection{Correlated Calls Occurrences}
Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.
\input{tables/stats}

\subsection{\code{TraversableOnce} Trait from Scala Standard Library}
Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.

@@

\subsection{Proofs}

\subsubsection{Representation of Micro Functions}
We start by presenting the proofs to the lemmas about the representation of micro functions.

@@

\subsubsection{Efficiency}
We will next introduce the complexity proof for the correlated-calls algorithm.
To satisfy the complexity requirements of the IDE algorithm, we need to provide
an implementation of the IDE lattice and micro-functions that satisfy the following
list of criteria~\cite{sagiv1996precise}:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
\efficient*
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice~\cite{nielson1999principles}.

@@

\subsubsection{Soundness and Precision}

@@

\subsubsection{Correlated-Call Receivers}
We will now present the proof for Lemma~\ref{lem:onlycorrrec} which shows that in a correlated-calls analysis, it is enough to consider only correlated-call receivers~$\rcc$.
